\par{
Iosif Angelidis is an IT professional with four (4) years of experience in software development stemming. His IT skills spam from IT programming with actual experience in C, C++, Java and Python, among other languages. This knowledge is gained both from self-motive to invest in new skill-sets and as part of his two years engagement in a Named Entity Recognizer thesis, which recognizes and extracts persons, organizations, geo-political entities, legal references, public documents and unofficial geographical landmarks found in the Government Gazette by utilizing Neural Networks and Deep Learning technologies.}

\par{During his military tour, Iosif has been occupied in the IT Division offering his experience in supporting 3 projects: MIP 3, ΣΧΚ and ΣΔΕΠ. This support came in the form of major refactoring, implementation of new features, optimization and critical performance gains, as well as general user support. His responsibilities further included the training of new staff and knowledge transferring.}

\par{Working at UBITECH since July 2020, he has contributed technical implementations, partially managed and delivered reports for H2020 projects \link{https://cordis.europa.eu/project/id/780938}{ChildRescue}, \link{https://cordis.europa.eu/project/id/760792}{FENIX}, \link{https://cordis.europa.eu/project/id/882897}{Search And Rescue}, \link{https://cordis.europa.eu/project/id/871703}{TheFSM}, \link{https://cordis.europa.eu/project/id/959879}{GLASS}, the EU accelerator DigiCirc project \link{https://digicirc.eu/irecirc/}{iReCirc } and ΕΣΠΑ projects \link{https://endorse.biosim.ntua.gr/}{ENDORSE }, 3DFollicleAI and PHAEDON. While improving his technical skills, he self-invests in learning management and software architect skills as well, resulting in him participating in the partial management of some of the aforementioned projects, as well as conducting requirement analysis, proposing conceptual, technical and deployment architectures and applying Agile methodology and User stories in the analysis process. Additionally, his contributions include deliverables writing, thorough technical documentations and demonstrators.}

\par{Iosif Angelidis has also shown particular interest in Artificial Intelligence courses both as a tutor (assistant professor) and as a practitioner. Last, but not least, Iosif has become a member of various communities among which the most notable ones pertain to the Management of Data and Information Knowledge Group (\link{http://www.madgik.di.uoa.gr}{MADgIK}) and the \link{http://ai.di.uoa.gr/}{AI group} of the University of Athens. }

\par{\textbf{Military obligations fulfilled.} }
