\sectionTitle{Working Experience}{\faSuitcase}
\begin{experiences}
\experience
    {present}   {IT Programmer}{Textkernel B.V.}{Amsterdam, Netherlands}
    {2022} {
                    \begin{itemize}
                    
                        \item Involved in the development lifecycle of Jobfeed.
                                                        
                        \item DevOps contributions such as dockerization, deployment and CI/CD pipelines.

                    \end{itemize}
                    }
                    {HTML 5, CSS 3, JavaScript, REST, Pandas, Scikit-learn, Elasticsearch, Cassandra, MySQL, Pycharm, Docker, CI/CD, Jenkins, Jira, Confluence}
\emptySeparator
\experience
    {2022}   {IT Programmer}{UBITECH LTD}{Athens, Greece}
    {2020} {
                    \begin{itemize}
                    
                        \item Involved in the development of a data market, Android applications, ABAC mechanisms, API Gateways,
                                                        semantic models design, hybrid encryption protocols, deep learning models and RESTful services.
                                                        
                        \item Tech lead, responsible for supervising the development of a number of projects and contributing to the code development.
                        
                        \item DevOps contributions such as dockerization, deployment and CI/CD pipelines.

                        \item Requirement analysis on functional, non-functional, technical, data, user requirements based on Agile methodology and User stories.
                        
                        \item Contributions to deliverables writing, technical documentation and demonstrators.
                        
                        \item Partial management of multiple H2020 and national projects co-founded by the EU.

                        \item Frequent coordination telcos with partners to meet the projects' needs.

                    \end{itemize}
                    }
                    {Requirement analysis, Agile methodology, User stories, architecture design, Java, Spring Boot, Quarkus, Keycloak, HTML 5, CSS 3, JavaScript, Leaflet JS, REST, IntelliJ, Android Stutio, Keras, Tensorflow, Pandas, Scikit-learn, ABAC, RBAC, ACL, Elasticsearch, MongoDB, MinIO, MySQL, PHPmyAdmin, Maven, Pycharm, Docker, CI/CD}
  \emptySeparator
  \experience
    {2020}   {IT Programmer}{Greek Army IT Support Center (Military Service IT Division)}{Athens, Greece}
    {2019} {
                    \begin{itemize}
                      \item Support of 3 projects: implementation of the Multilateral Interoperability Protocol 3.0, the Crisis Management System
                      and the Information Management-Control System.

                      \item Major code refactoring, optimizations, critical performance gains (e.g., database requests taking about 3 seconds compared to 15 minutes), 
                      implementation of new features.

                      \item Worked on classified data and geospatial information.

                      \item Responsible for training new staff and providing user support for the platforms.
                    \end{itemize}
                    }
                    {Java, EJBs, JSF, PrimeFaces, Oracle 11g/12c, Hibernate, HTML 5, CSS 3, JavaScript, Leaflet JS, REST, SOAP, XML, SQL Server Management Studio, Toad, WildFly/JBoss, IntelliJ}
  \emptySeparator
  \experience
    {2019} {IT Programmer}{University of Athens}{Athens, Greece}
    {2017}    {
                    \begin{itemize}
                      \item Developed and maintained a Named Entity Recognizer in the context of MSc thesis ``Named Entity Recognition and Linking in Greek Legislation''.

                      \item Extraction of persons, organizations, geo-political entities, legal references, public documents and unofficial geographical landmarks found in the Government Gazette.

                      \item Utilization of Neural Networks and Deep Learning techniques.
                    \end{itemize}
                    }
                    {Python, Keras, TF, SciKit Learn, Numpy, Pandas, (Geo/st)SPARQL, REST, HTML 5, CSS 3, RDF, OWL, Maven, PyCharm}
\end{experiences}
